{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-28 paper/paper.tex
added first two paragraphs of FSI

\subsection{Observational Determinism for Concurrent Program Security}
\subsection{Flexible Scheduler-Independent Security}

>>>>

\subsection{Observational Determinism for Concurrent Program Security}
\subsection{Flexible Scheduler-Independent Security\cite{Mantel10}}
This approach developed by Mantel and Sudbrock has the goal to be on the one hand
scheduler independent and on the other not too restrictive (i.e. does not treat
obviously secure programs as insecure).

To reach this goal they model the scheduling explicit but general enough to apply
to a wide class of common schedulers. So rather than talking about program states,
they introduces system configurations which contain the list of threads the global
memory and the scheduler state. The scheduler is able to store information in its
state and can retrieve input (e.g. the number of active threads). Based on this
information the scheduler makes decisions. To cover probabilistic schedulers the
decision making of the scheduler and the execution of the program is probabilistic.
